Social Learning in the Media: The Importance of Bias for Trust Between Media Firms

### 2014-07-05 paper/paper.tex
full posterior

 Unfortunately, this does not work in the case considered above because each firm can observe the reports of their fellow firms, so it is possible you may observe duplicate information.  To account for this we need to account for how much firms trust each other and how likely they are to borrow information from other firms.  Fortunately, you have a measure of how much likely it is that each firm will incorporate the reports of another firm into their report, $p_j(\text{high}_i|\hat{\textbf{s}}_{it})$.  We could modify the above posterior to account for this, let $\gamma_ij$ represent $p_j(\text{high}_i|\hat{\textbf{s}}_{it})$
 x
 \[p(R|\hat{\textbf{s}}) \propto (1-\gamma_{12})(1-\gamma_{13})...(1-\gamma_{1N})p(\hat{s}_1|R)...(1-\gamma_{N1})(1-\gamma_{N2})...(1-\gamma_{NN-1})p(\hat{s}_N|R)p(R)\]

@@

\[\alpha_{it} \sim N(\textbf{\alpha}_{t-1}^T \gamma, \delta^2I)\]

$\textbf{\alpha}$ is a vector of the $\alpha$ parameter for each of the $N$ agents, and $\gamma$ is an $N$ dimensional vector of weights for the $N$ agents.  That is, $\alpha_{it}$ is drawn from a weighted sum of the $\alpha$ values for each agent in the prior period.  $\gamma$ gives an estimate of the impact that each agent has on the topic distribution of the $i$th agent.  We use $\gamma$ to represent our trust value discussed above.  Unfortunately, this generating process does not have a conjugate form so we cannot using Gibbs sampling as used commonly with LDA.  Instead we must use a more complicated Metropolis Hastings algorithm to estimate $\gamma$.

>>>>

 Unfortunately, this does not work in the case considered above because each firm can observe the reports of their fellow firms, so it is possible you may observe duplicate information.  To account for this we need to account for how much firms trust each other and how likely they are to borrow information from other firms.  Fortunately, you have a measure of how much likely it is that each firm will incorporate the reports of another firm into their report, $p_j(\text{high}_i|\hat{\textbf{s}}_{it})$.  We could modify the above posterior to account for this, let $\gamma_ij$ represent $p_j(\text{high}_i|\hat{\textbf{s}}_{it})$
 x
 \[p(R|\hat{\textbf{s}}) \propto (1-\gamma_{12})(1-\gamma_{13})...(1-\gamma_{1N})p(\hat{s}_1|R)...\]

 \[(1-\gamma_{N1})(1-\gamma_{N2})...(1-\gamma_{NN-1})p(\hat{s}_N|R)p(R)\]

@@

\[\alpha_{it} \sim N(\alpha_{t-1}^T \gamma, \delta^2I)\]

$\alpha$ is a vector of the $\alpha$ parameter for each of the $N$ agents, and $\gamma$ is an $N$ dimensional vector of weights for the $N$ agents.  That is, $\alpha_{it}$ is drawn from a weighted sum of the $\alpha$ values for each agent in the prior period.  $\gamma$ gives an estimate of the impact that each agent has on the topic distribution of the $i$th agent.  We use $\gamma$ to represent our trust value discussed above.  Unfortunately, this generating process does not have a conjugate form so we cannot using Gibbs sampling as used commonly with LDA.  Instead we must use a more complicated Metropolis Hastings algorithm to estimate $\gamma$.

\newpage
\appendix

\section{Full Conditionals}

\[p(\gamma_i | \mu, \xi^2) = N(\mu, \xi^2I)\]

\[p(\alpha_{it} | \text{\boldmath$\alpha$}_{t-1}. \gamma_i, \delta^2) = N(\text{\boldmath$\alpha$}^T_{t-1} \gamma_i, \delta^2I)\]

\[p(\beta_t | \beta_{t-1}, \sigma^2) = N(\beta_{t-1}, \sigma^2I)\]

\[p(\theta_{itd} | \alpha_{it}, a^2) = N(\alpha_{it}, a^2)\]

\[p(z_{itnd}| \theta_{itd}) = Mult(\pi(\theta_{itd}))\]

\[p(w_{itnd} | \beta_t, z_{itnd}) = Mult(\pi(\beta_t^{z_{itnd}}))\]

\[p(\theta, \text{\boldmath$\gamma$}, \text{\boldmath$\alpha$}, \text{\boldmath$\beta$}, \textbf{z} | \textbf{w}) \propto \prod_{i=1}^M \prod_{t=1}^T \prod_{n=1}^N \prod_{d=1}^D p(w_{itnd}|z_{itnd}, \beta_t) p(\beta_t | \beta_{t-1}, \sigma^2) p(z_{itnd}|\theta_{itd})\]

\[p(\theta_{itd}|\alpha_{it},a^2)p(\alpha_{it}|\text{\boldmath$\alpha$}_{t-1}, \gamma_i, \delta^2) p(\gamma_i | \mu, \xi^2)\]

\subsection{Posterior Specification for $z_i$}
